\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[sorting=none]{biblatex}
\addbibresource{papers.bib}
\usepackage{csquotes}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/jiradett/}{\Large Jiradett Kerdsri, Ph.D.}} & Email : \href{mailto:jiradett@gmail.com}{jiradett@gmail.com}\\
  \href{www.linkedin.com/in/jiradett/}{linkedin.com/in/jiradett/} & Mobile : +61 4 5118 9377 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Data Engineer Lead}{Melbourne, Australia}
  {Cancer Council Victoria}{July 2023 - Present}
  \resumeItemListStart
  \resumeItem{Data Architecture \& Modernization}{
  \begin{itemize}
    \item Led the development of a Snowflake data warehouse as the single source of truth, centralizing and streamlining data management.
    \item Modernized the CRM platform by migrating to Salesforce, enhancing data accessibility and customer relationship management.
    \item Built and optimized data pipelines using Azure Data Factory and Microsoft Fabric, ensuring efficient data flow and transformation.
    \item Implemented CI/CD practices on DevOps, automating deployment processes and improving system reliability.
    \item Collaborated with stakeholders to design and present data solutions, including visualizations and relational databases.
    \item Took ownership of the end-to-end data project lifecycle, from strategy and road-mapping to architecture and implementation.
    \item Participated in agile teams to deliver key features and functionalities.
  \end{itemize}
  }
\resumeItemListEnd
  \resumeSubheading
  {Data Engineer}{Melbourne, Australia}
  {Parliament of Victoria}{Dec 2021 - July 2023}
  \resumeItemListStart
  \resumeItem{Data Strategy \& Modernization}{
  \begin{itemize}
    \item Led the design, development, and deployment of data platform solutions, including ETL and data analysis.
    \item Spearheaded data management infrastructure renovation, driving automation in data integration and management.
    \item Migrated on-prem solutions to cloud services, modernizing the data environment and improving scalability.
    \item Developed data products using version control and DevOps practices to ensure efficient and reliable delivery.
    \item Utilized Power BI and Microsoft Fabric for advanced data visualization and integration, enhancing data accessibility and insights.
    \item Owned Azure API Management and Azure Service Bus tools, ensuring seamless data flow and integration.
  \end{itemize}
  }
  \resumeItem{End-to-End Data Engineering}{
  \begin{itemize}
    \item Built and operationalized data pipelines, collaborating with stakeholders for continuous improvement of enterprise data frameworks.
    \item Used modern data preparation and integration tools.
    \item Automated data integration flows and monitored schema changes to enhance data reliability.
  \end{itemize}
  }
  \resumeItem{Collaboration \& Governance}{
  \begin{itemize}
    \item Partnered with business and IT teams to refine data requirements and promote data capabilities across the organization.
    \item Ensured data governance and compliance, contributing to a curated data catalog for governed reuse.
    \item Planned and initiated the creation of a data warehouse to serve as a single source of truth for siloed data, enhancing data consistency and accessibility.
  \end{itemize}
  }
\resumeItemListEnd

    \resumeSubheading
      {Deputy Director of Data Analytics}{}
      {Bank of Thailand}{Oct 2018 - Oct 2021}
      \resumeItemListStart
      \resumeItem{Principal Data Scientist \& AI/ML Specialist}{
      \begin{itemize}
        \item Led a team of data scientists to leverage AI and machine learning on granular and alternative data, enhancing insights beyond traditional analytics.
        \item Executed time series forecasting projects using advanced algorithms to predict trends and anomalies.
        \item Developed convolutional neural networks (CNNs) for image processing, achieving high accuracy in classification and detection tasks.
        \item Integrated NLP and text mining to extract insights from unstructured data.
        \item Collaborated with data engineers to design scalable data pipelines for time series and image data analysis.
        \item Mentored junior data scientists in machine learning techniques, fostering a culture of innovation.
      \end{itemize}
      }
      \resumeItem{Data Architect \& Strategic Leader}{
      \begin{itemize}
        \item Played a pivotal role in shaping the enterprise data architecture, ensuring it supports the advanced needs of AI and machine learning projects.
        \item Directed the data engineering processes to build scalable, efficient data pipelines that feed into AI and machine learning models, facilitating real-time data processing and analysis.
        \item Led strategic initiatives to advance the organization toward a fully data-driven model, with a strong focus on integrating AI and machine learning into the core decision-making processes.
        \item Worked closely with stakeholders to align data architecture and engineering efforts with business objectives, ensuring the deployment of AI and machine learning models that meet specific organizational needs.
      \end{itemize}
      }
  \resumeItemListEnd

    \resumeSubheading
      {Director of Data Communication}{}
      {Defense Technology Institute}{Jul 2009 - Oct 2018}
      \resumeItemListStart
      \resumeItem{Director of Research}{
      \begin{itemize}
        \item Led and managed a data communication laboratory, overseeing research and functional projects in areas such as Big Data, AI, Machine Learning, and Computer Vision.
        \item Directed AI/ML research initiatives, particularly in computer vision, and drove advancements in opportunistic networks, MANET, and tactical networks.
        \item Managed software development projects using JAVA, PHP, and Python, ensuring the successful implementation of research findings into functional software solutions.
        \item Acted as project manager for research projects, ensuring alignment with organizational goals and timely publication of research outcomes.
        \item Maintained and exceeded organizational KPIs related to research publications, contributing to the organization's reputation and academic impact.
        \item Organized and led international conferences on defense research, facilitating knowledge exchange and collaboration within the global research community.
        \item Provided expert knowledge management for basic research, ICT projects, and research publications, supporting strategic initiatives.
        \item Supported the Director of Research and Development with detailed technical reports, providing insights and recommendations based on the latest research findings.
        \item Coached and mentored associate researchers in research methodology, fostering a culture of continuous learning and innovation.
        \item Suggested and implemented technology initiatives for defense research projects, driving the adoption of cutting-edge AI and ML techniques in defense applications.
      \end{itemize}
      }
  \resumeItemListEnd

    \resumeSubheading
      {Lecturer}{}
      {International Hospitality Management School VATEL}{May 2013 - Sep 2018}
      \resumeItemListStart
        \resumeItem{Invited lacturer}
          {\begin{itemize}
              \item Implemented and managed ICT curriculum for VATEL.
              \item Teaching information technology for the hospitality business course.
            \end{itemize}}
      \resumeItemListEnd

      \resumeSubheading
      {IT Administrator \& Sales}{Melbourne, Australia}
      {Something Aussie}{Jan 2008 - Jan 2009}
      \resumeItemListStart
        \resumeItem{IT and Sales support}
          {\begin{itemize}
            \item Managed IT infrastructure for the shop, including online payment, PoS, CRM, and website.
            \item Responsible for sales and marketing.
            \item Maintained the website and online orders.
            \item Supported the PR team, and social media marketing.
          \end{itemize}}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{}
      {Ministry of Defence}{Mar 2003 - Jul 2009}
      \resumeItemListStart
        \resumeItem{Programming and System Administrator}
          {
            \begin{itemize}
              \item Implemented and develop the application for Command, Control, Communications, Computers, \& Intelligence (C4I) system.
              \item Worked on data analytics for Geographic Information System (GIS) and spatial analysis.
              \item Worked with US Department of Defence on Multinational Communications Interoperability Program (MCIP).
              \item Developed communication application for Counter Terrorist Operations Center (CTOC).
              \item Worked with the United Nations for the peacekeeping mission.
            \end{itemize}}
      \resumeItemListEnd

      \resumeSubheading
      {Student Pilot}{}
      {Air Force}{Oct 1999 – Oct 2000}
      \resumeItemListStart
        \resumeItem{Tranied Aircrafts}{        
          \begin{itemize}
          \item PAC CT/4 Airtrainer.
          \item Bell 206 JetRanger/LongRanger Multipurpose utility helicopter.
        \end{itemize}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  %-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Sirindhorn International Institute of Technology}{Pathumthani, Thailand}
    {Ph.D. in Engineering and Technology}{2011 - 2015}
  \resumeSubheading
    {University of Melbourne}{Victoria, Australia}
    {Master in Geographic Information Technology}{2008 - 2009}
  \resumeSubheading
    {US Naval Postgraduate School}{California, USA}
    {Master in Computer Science}{2001 - 2003}
  \resumeSubheading
    {Air Force Academy}{Bangkok, Thailand}
    {Bachelor in Civil Engineering}{1994 - 1999}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{QuantSoftware Toolkit}
%       {Open source python library for financial data analysis and machine learning for finance.}
%     \resumeSubItem{Github Visualization}
%       {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%     \resumeSubItem{Recommendation System}
%       {Music and Movie recommender systems using collaborative filtering on public datasets.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%   \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\section{Publications}
\begin{refsection}
  \nocite{Kerdsri2017}
  \nocite{doi:10.1155/2015/819178}
  \nocite{Kerdsri2013}
  \nocite{journal2013}
  \nocite{waset2011}
  \AtNextBibliography{\small}
	\printbibliography[title={Journals}]
\end{refsection}

\begin{refsection}
	\nocite{Kerdsri2018}
  \nocite{7886152}
  \nocite{7332543}
  \nocite{Kerdsri2012}
  \nocite{6427357}
  \nocite{6174610}
  \nocite{waset2010}
	\AtNextBibliography{\small}
	\printbibliography[title={Conference Proceedings}]
\end{refsection}

\begin{refsection}
  \nocite{book2013}
  \nocite{book2013a}
  \nocite{book2012}
  \nocite{book2012a}
  \nocite{book2012b}
  \nocite{book2007}
  \nocite{kerdsri2003snmp}
	\AtNextBibliography{\small}
	\printbibliography[title={Books}]
\end{refsection}

%-----------Certificates-----------------
\section{Certificates}
  \resumeSubHeadingListStart
  \resumeSubItem{Hands On Essentials - Data Engineering}{Snowflake}
  \resumeSubItem{DP-500T00 -Designing and Implementing Enterprise-scale Analytics Solutions using Microsoft Azure and Microsoft Power BI}{Advanced Training}
  \resumeSubItem{DP-203T00 - Data Engineering on Microsoft Azure}{Advanced Training}
  \resumeSubItem{Microsoft Azure for Data Engineering}{Coursera}
  \resumeSubItem{Azure Service Bus for Developers}{Udemy}
  \resumeSubItem{Apache Spark SQL for Data Analyst}{Coursera}
  \resumeSubItem{ISO/IEC 27701:2019}{BSI}
  \resumeSubItem{Deploy Machine Learning \& NLP Models with Dockers (DevOps)}{Udemy}
  \resumeSubItem{The Data Scientist’s Toolbox by Johns Hopkins University}{Cousera}
  \resumeSubItem{Deep Learning Institute Fundamentals Workshop}{NVIDIA}
  \resumeSubItem{Power BI}{DataCube}
  \resumeSubItem{Using Python to Access Web Data}{Coursera}  
  \resumeSubItem{Data Analytics and Big Data using Opensource}{Kasetsart University}
  \resumeSubItem{Introduction to Data Science in Python}{Coursera}   
  \resumeSubItem{Big Data Analytic using Hadoop and Spark}{IMC Institute}
  \resumeSubItem{Leadership}{FranklinCovey}
  \resumeSubItem{Smart Professional Image for Project Manager Program}{John Robert Powers}
  \resumeSubItem{Python for Everybody Specialization}{Coursera}
  \resumeSubItem{Big Data Training Course}{Udemy}         
  \resumeSubHeadingListEnd

%-----------Consultancy Roles-----------------

  \section{Data Consultant}
  \resumeSubHeadingListStart
  \resumeSubItem{Pro Technical Info Services Co.Ltd.}{Provide consultative guidance on deploying big data analytics concepts to project.}
  \resumeSubItem{ENergy SOLution (ENSOL)}{Provide consultative guidance on collecting and analyze IoT data from various sensors.}     
  \resumeSubHeadingListEnd

%-----------Speaking-----------------
\section{Speaking Engagements}
  \resumeSubHeadingListStart
  \resumeSubItem{Chief Data Scientist Conference}
    {Keynote Speaker: Enabling data generation to feed the need of machine learning, Bangkok, Thailand, 2020.}
    \resumeSubItem{World AI Show}
      {Panelist: Enabling Innovation Through Effective Digital Transformation, Intercontintental, Bangkok, Thailand, 2019.}
    \resumeSubItem{Enterprise AI Conference}
      {Keynote Speaker: Data Analytics for Central Bank, Grand Mercure Bangkok Fortune, 2019.}
     \resumeSubItem{2nd Annual Analytics Leader Summit}
      {Keynote Speaker and Panelist: Data Analytics for Bank of Thailand, Mercure Manila, Philippines, 2019.}
    \resumeSubItem{3rd Annual Analytics Leader Summit}
      {Keynote Speaker and Panelist: Data Analytics for Bank of Thailand, Ayana Mid Plaza, Jakara, Indonesia, 2019.}
    \resumeSubItem{1st Annual Analytics Leader Summit}
      {Keynote Speaker: Military AI Research, Bangkok, Thailand, 2019.}
    \resumeSubItem{SmartCom 2018 -The 5th International Workshop on Smart Wireless Communications}
      {Invited Talk: Opportunistic Network Informatics using Deep Learning, Mandarin Hotel, Bangkok, Thailand, 2018.}

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Selected Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Unfit Banknote Classification [2019]}
      {Use Convolutional Neural Network (ConvNet/CNN) for modeling the machine learning classification to identify the unfit note for banknote production.}
    \resumeSubItem{Computer Vision for Vehicle detection [2017]}
      {Develop a deep learning program to detect the vehicle (brand, model, color and year) for CCTV using Python and TensorFlow.}
    \resumeSubItem{Organizing international conference on defense technology (ACDT)}
      {Responsible for organizing Asian Conference on Defence Technology (ACDT) which started from 2015 and held annually:
      \resumeItemListStart
      \resumeItem{The First Asian Conference on Defence Technology}{Huahin, Thailand, 23 – 25 April 2015.}
      \resumeItem{The Second Asian Conference on Defence Technology and The First Pacific Rim International Workshop on Defence, Safety, and Security Technology}{Chiang Mai, Thailand, 21 – 23 January 2016.}
      \resumeItem{The Third Asian Conference on Defence Technology}{Phuket, Thailand, 18 – 20 January 2017.}
      \resumeItem{The Fourth Asian Conference on Defence Technology}{Tokyo, Japan, 29 November – 1 December 2017.}
      \resumeItem{The Asian Conference on Defence Technology 2018}{Hanoi, Vietnam, 25 - 27 October 2018.}
      \resumeItemListEnd
      }
      
    \resumeSubItem{Intelligence Data-Link Analysis for Checkpoint Operations (IDA-CHO) [2017-2018]}
      {The co-research project with National Electronics and Computer Technology Center (NECTEC) developed on:
      - Graph Database: Neo4j
      - Link Analysis: Python, Cypher (Neo4j's graph query language)
      - Graph Visualization: CytoScape, PostMan, WebApp2, JinJa2, Javascript, Bootstrap}
    \resumeSubItem{Internal ballistic simulation software [2013-2015]}
      {Develop a simulation software for rocket internal ballistic using JAVA.}
    \resumeSubItem{Common Operation Picture (COP) [2012-2014]}
      {Develop a situational awareness application for Thai Armed Forces based on C\# and Google Map Enterprise with the Data Distribution Service (DDS) communication..}
    \resumeSubItem{Multinational Communications Interoperability Program (MCIP) [2008]}
      {The program to test the interoperability for communication systems among US and ASEAN countries.}
    \resumeSubItem{Management information system (MIS) for the criminal court [2004-2005]}
      {Implement the paperless information system to replace conventional system. The system was deployed on JSP and Oracle database.}
    \resumeSubItem{Fabric pattern selection software [2003-2004]}
      {Develop a fabric pattern selection software for The Foundation For the Promotion of Supplementary Occupations and Related Techniques under the Royal Patronage of Her Majesty the Queen using PHP.}
    \resumeSubItem{Negotiations software for anti-terrorist communication system [2003-2004]}
      {Implement a software for multi-users communications (Twitter-like) for negotiations in anti-terrorist mission for Counter Terrorist Operations Center (CTOC) using PHP.}
  \resumeSubHeadingListEnd
\end{document}
