\documentclass[12pt]{article}
\usepackage{design_ASC}
\usepackage[english]{babel}
\usepackage[sorting=none]{biblatex}
\addbibresource{papers.bib}


\setlength\parindent{0pt} %% Do not touch this

%% -----------------------------
%% TITLE
%% -----------------------------
\title{Selection Criteria } %% Assignment Title

\author{Jiradett Kerdsri, Ph.D.\\ %% Student name
for\\ %% Code and course name
\textsc{University of New England}
}

\date{\today} %% Change "\today" by another date manually
%% -----------------------------
%% -----------------------------

%% %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\setlength{\droptitle}{-5em}    
%% %%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle

% --------------------------
% Start here
% --------------------------

% %%%%%%%%%%%%%%%%%%%
\section*{Knowledge and Education}
% %%%%%%%%%%%%%%%%%%%

% %%%%%%%%%%%%%%%%%%%
\subsection*{1. A research higher degree at doctoral level in Computer Science, Data Science, or a related field.}
% %%%%%%%%%%%%%%%%%%%
{\bfseries In my education and work background, I have been experienced in all positions under the selection criteria:}

\begin{itemize}
    \item I have a master of computer science and a Ph.D. in engineering and technology (specialize in computer networking).
    \item I have worked as a research director at a data communication laboratory for 10 years on the topic of Big data, Data analytics (data science), Artificial Intelligence (AI), Machine (deep) Learning (mainly on Computer Vision), Opportunistic Networks, MANET, Tactical Network, etc.
    \item Currently, I am working as a chief data scientist leading the core-data scientist team to make use of micro/granular data and alternative data (Big Data) to augment insights found from aggregated data through the use of artificial intelligence, machine (deep) learning, text processing, and network theory.

\end{itemize}

\subsection*{2. Strong technical skills related to Computer Science or Data Science such as programming, data analysis and algorithm development, applied in the context of research and scholarship.}
{\bfseries I have computer science technical skill experience from several research projects when I was a software developer and researcher for the domain of:}
\begin{itemize}
    \item \textbf{Programming}: Python, R, Java, PHP, JSP, C++, Ruby on Rails, etc.
    \item \textbf{Database}: MySQL, MS SQL Server, Oracle, Hadoop.
    \item \textbf{Cloud technologies}: AWS, GCP, Azure Cloud, Databricks.
    \item \textbf{Computer OS}: Linux, Unix, Windows, Mac.
    \item \textbf{Visualization software}: Tableau, Microsoft Power BI
    \item \textbf{Machine learning}: Convolutional Neural Networks, Time Series, Classification, Regression, etc.
\end{itemize}


% %%%%%%%%%%%%%%%%%%%
\section*{Delivers and achieves results}
% %%%%%%%%%%%%%%%%%%%
\subsection*{3. A demonstrated capacity to consistently and successfully lead research projects and build productive and collaborative, cross-disciplinary research relationships in Computer Science or Data Science}

{\bfseries I have been a director of a data communication laboratory and leading researcher project on many occasions with academic and industries parters such as:}
\begin{itemize}
    \item \textbf{Intelligence Data-Link Analysis for Checkpoint Operations}: This is a  co-research project with the National Electronics and Computer Technology Center aiming to implement a graph database of analyzing terrorist activities developed on: Graph Database: Neo4j, Link Analysis: Python, Cypher (Neo4j graph query language), Graph Visualization: CytoScape, PostMan, WebApp2, JinJa2, Javascript, Bootstrap.
    \item \textbf{Common Operation Picture}: This research project is to develop a situational awareness application for the ministry of defense on C\# and Google Map Enterprise with the Data Distribution Service (DDS) communication.
    \item \textbf{Unfit Banknote Classification}: This research project use Convolutional Neural Network (ConvNet/CNN) for modeling the machine learning classification to identify the unfit note for banknote production.
    \item \textbf{Computer Vision for Vehicle detection}: This research project is to develop a deep learning program to detect the vehicle (brand, model, color, and year) for CCTV using Python and TensorFlow.
\end{itemize}


% %%%%%%%%%%%%%%%%%%%
\section*{Acts with Courage and Integrity}
% %%%%%%%%%%%%%%%%%%%
\subsection*{4. An established research track record in Computer Science, Data Science, or a related field, as evidenced by publications, research grants and postgraduate supervision.}

{\bfseries I have been granted research funding in a couple of projects such as Intelligence Data-Link Analysis for Checkpoint Operations or Common Operation Picture. Additionally, I have been a chief of staff to organize an annual international conference on defense technology started in 2015:}
\begin{itemize}
    \item The First Asian Conference on Defence Technology, Huahin, Thailand, 23 – 25 April 2015.
    \item The Second Asian Conference on Defence Technology and The First Pacific Rim International Workshop on Defence, Safety, and Security Technology, Chiang Mai, Thailand, 21 – 23 January 2016.
    \item The Third Asian Conference on Defence Technology, Phuket, Thailand, 18 – 20 January 2017.
    \item The Fourth Asian Conference on Defence Technology, Tokyo, Japan, 29 November – 1 December 2017.
    \item  The Asian Conference on Defence Technology 2018, Hanoi, Vietnam, 25 - 27 October 2018.
\end{itemize}

{\bfseries My publication records are as follows:}

\begin{refsection}
    \nocite{Kerdsri2017}
    \nocite{doi:10.1155/2015/819178}
    \nocite{Kerdsri2013}
    \nocite{journal2013}
    \nocite{waset2011}
    \AtNextBibliography{\small}
    \printbibliography[title={Journals}]
  \end{refsection}

  \begin{refsection}
    \nocite{Kerdsri2018}
    \nocite{7886152}
    \nocite{7332543}
    \nocite{Kerdsri2012}
    \nocite{6427357}
    \nocite{6174610}
    \nocite{waset2010}
    \AtNextBibliography{\small}
    \printbibliography[title={Conference Proceedings}]
  \end{refsection}
  
  \begin{refsection}
    \nocite{book2013}
    \nocite{book2013a}
    \nocite{book2012}
    \nocite{book2012a}
    \nocite{book2012b}
    \nocite{book2007}
    \nocite{kerdsri2003snmp}
    \AtNextBibliography{\small}
    \printbibliography[title={Books}]
  \end{refsection}



% %%%%%%%%%%%%%%%%%%%
\section*{Delivers and achieves results}
% %%%%%%%%%%%%%%%%%%%
\subsection*{5. Evidence of high-quality teaching across all programs of study in Computer or Data science, and engagement with technology for innovative teaching, as evidenced by student evaluations and other relevant documentation.}

{\bfseries }I have been an invited lecturer on information technology at Hotel \& Tourism Business School, Silpakorn International University for five years. During those years, I have been supervised many students for senior research projects for a course on information technology for the hospitality business.



\subsection*{6. Demonstrated experience in supervision of Honours and postgraduate research projects including PhD research.}

{\bfseries }I have been a mentor to supervise junior Ph.D. researchers at the data communication laboratory for 10 years. 


% %%%%%%%%%%%%%%%%%%%
\section*{Communicates with Influence}
% %%%%%%%%%%%%%%%%%%%
\subsection*{7. Excellent communication, teamwork and organisational skills, and the ability to relate well to colleagues and students.}

{\bfseries}During my career, I have been a project manager, a chief of conference organizing,  a laboratory leader, and a guest lecturer that presenting strong communication, teamwork, and organizational skills.

% %%%%%%%%%%%%%%%%%%%
\section*{Develops and Maintains Relationships}
% %%%%%%%%%%%%%%%%%%%

\subsection*{8. Demonstrated ability to undertake service roles within an academic discipline.}
{\bfseries} For my 20 years of experience with various industries and academics, I have been taken many roles to service each position such as project manager for the basic research project for defense technology institute, or chief data scientist to supervise junior data scientists at the Bank of Thailand.

% %%%%%%%%%%%%%%%%%%%
\section*{Desirable}
% %%%%%%%%%%%%%%%%%%%

\subsection*{1. Experience in a tertiary teaching setting using flexible modes of course delivery.}
{\bfseries} I have been a guest lecturer for 5 years which experiencing in the on-site course and online course teaching.

\subsection*{2. Background and/or knowledge of applied Computer Science or Data science in agricultural, ecological, health or sports science disciplines.}
{\bfseries} At the Bank of Thailand, I have worked on many projects related to agricultural discipline such as the digital economy for sustainable agriculture project to implement the rice production model using MGBoost.



\end{document}